Optifcal Observations of an Extraordinarily Young Type Ia Supernova iPTF16abc

### 2017-06-06 doc/ms.tex
Update the text to reflect new values following an improved fit to the SALTs parameters.

To determine the brightness and time of $B$-band maximum for 
iPTF16abc, we fit the P48 and P60 light curves with the \texttt{sncosmo} software package.\footnote{The
  \texttt{sncosmo} Python module is available at
  \url{https://sncosmo.readthedocs.io/en/v1.4.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
\ref{sec:reddening} and $R_V=3.1$.

We determine the time of rest-frame \textit{B}-band maximum to be 
 $\textrm{MJD}_{max}=57499.65\pm0.02$, the coefficient
of the zeroth principle component $x_0=0.0275\pm0.0002$, the
coefficient of the first principle component $x_1=1.200\pm0.043$, and
the color term $c=-0.3353\pm0.0054$. The best-fit model also gives an
unreddened apparent peak magnitude of $m^*_{B}=14.4\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
the SN rest frame.

For convenience, in the following sections, we define the best-fit
value $\textrm{MJD}_{max}=57499.65$ as phase $t=0$.

@@

After establishing iPTF16abc as a normal SN Ia, we use the latest
calibration \citep{2014A&A...568A..22B} of the Phillips relation
\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
distance modulus $\mu=34.66\pm0.03\,\textrm{mag}$ to the SN, provided
that the host galaxy of iPTF16abc has a stellar mass less than
$10^{10}\sm$.

>>>>

To determine the brightness and time of $B$-band maximum for 
iPTF16abc, we fit the P60 light curves with the \texttt{sncosmo} software package.\footnote{The
  \texttt{sncosmo} Python module is available at
  \url{https://sncosmo.readthedocs.io/en/v1.5.x/}.} This fit includes a SALT2 template \citep{2007A&A...466...11G} modified by the line-of-sight extinction
curve \citep{1999PASP..111...63F} with $E(B-V)$ values from Section
\ref{sec:reddening} and $R_V=3.1$.

We determine the time of rest-frame \textit{B}-band maximum to be 
 $\textrm{MJD}_{max}=57499.54\pm0.23$, the coefficient
of the zeroth principle component $x_0 = XXX \pm XXX$, the
coefficient of the first principle component $x_1 = 0.9655 \pm 0.0003$, and
the color term $c = 0.012 \pm 0.029$. The best-fit model also gives an
unreddened apparent peak magnitude of $m^*_{B}=15.6\,\textrm{mag}$ \ycao{uncertainties on Bmax?} in
the SN rest frame.

For convenience, in the following sections, we define the best-fit
value $\textrm{MJD}_{max}=57499.54$ as phase $t=0$.

@@

After establishing iPTF16abc as a normal SN Ia, we use the latest
calibration \citep{2014A&A...568A..22B} of the Phillips relation
\citep{1993ApJ...413L.105P} using $m^*_{B}$, $x_1$ and $c$ to derive a
distance modulus $\mu = 34.72 \pm 0.09 \,\textrm{mag}$ to the SN, provided
that the host galaxy of iPTF16abc has a stellar mass less than
$10^{10}\sm$. We note that a more massive host galaxy would result in a larger inferred distance modulus that is nevertheless consistent within the uncertainties.
